---
title: "League of Legends Project"
author: "Group 9 - Ziyue Chen, Rishabh Kaushik, Vera Meanti, Aman Sharma, Sarah Wu, Stephen Zhu"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

(1) A statement of the question or purpose. What problems or questions
    did you set out to analyse? What were the key issues raised?

League of Legends is a Multiplayer Online Battle Arena (MOBA) game. For
this project we have data on the first 10 minutes of 10,000 games. All
of these games are diamond-ranked, which means the players are in the
top 1.5% to 0.19% of players worldwide. The game lasts approximately 20
to 30 mins, there are two teams (Red vs Blue), with 5 players each. The
goal of the game is to take down the enemy Nexus.

The main variables in our data are: - Game_ID -\> unique identifier for
each game - Blue_wins -\> '0' if the Blue Team won the game, '1' if the
Red team won. - Other 19 variables per team (38 total) -\> Statistics
and features of the game collected after 10 minuted of playing. These
include number of kills, deaths, average experience and level and more.

Our purpose is to explore what is the best strategy in the first 10mins
of playing, to win League of Legends.

(2) The background and preparation for conducting the project. How did
    you prepare for the project? What sources or background readings did
    you consult? What information did you use in developing your ideas
    from the conceptual stage to the finished project?

As not all of us were familiar with the League of Legends game, we had
to conduct some research to really understand the game and the variables
in the dataset. All our group members played the game to immerse
ourselves in the League of Legends world and understand what stories
could be told from the data.

(3) Methodology. What did you do, and how did you do it? What
    statistical techniques did you use --- for instance, scatterplots,
    correlation, confidence intervals, linear/logistic regression?

After loading, inspecting and cleaning the dataset we conducted some
basic exploratory data analysis (EDA) by plotting pairwise correlations,
linear and logistic regression models to investigate the underlying
relationships between independent variables and with the dependent
variable (which team wins).

(4) Results and conclusions. This is where you summarise and present
    your data analyses and communicate your main results. What did you
    find out? This might include tables, graphs, or verbal summaries.
    What did you learn about the problem or question you set out to
    investigate?

What we learnt is that statistically it is very clear to predict which
team has the advantage, and therefore their chance of winning, after
only 10 minutes of a game that can last 30-40 minutes.

In the interests of a players efficiency, choosing to surrender after 10
minutes may be a wise move despite the fact it locks in a loss, but
saves the players the additional time of playing a game that they are
highly likely to lose.

(5) Discussion and critique. What did you learn about the process of
    carrying out your project? What went wrong, and how could you
    improve it next time? For instance, did any sources of bias creep
    into your survey or experiment? What advice would you give future
    students?

League of Legends is a popular game. According to LeagueFeed, it had
over 100 million players in 2020. However, many of our team were not
very familiar with the game and this made the process of storytelling
and turning data into valuable insight quite challenging, especially if
our audience is those who are highly knowledgable and skilled at the
game. One benefit of this situation though is that most of us would be
quite unbiased when it comes to recommending a game strategy because we
do not have personal anecdotal experience that may influence which
conclusions we wish to draw. Moreover, we obtained this dataset from
Kaggle and some cleaning had already been done. While this was helpful
for us, it also meant we have less transparency and understanding of the
original dataset and must have faith in the integrity of whoever
uploaded it.

```{r libraries, include=FALSE}
library(tidyverse)
library(extrafont)
library(vroom)
library(skimr)
library(sf)
library(GGally)
library(rsample)
library(caret)

loadfonts(device="pdf") 
```

## Loading the Dataset

```{r}
#Loading the dataset
raw_lol_data <- read.csv("high_diamond_ranked_10min.csv")

#Initial cleaning of names and dropping any na's 
raw_lol_data <- raw_lol_data %>% 
  janitor::clean_names() %>% 
  drop_na()
```

# Cleaning the Data

```{r Vera}

# Checking that variables are all stored as the right type 
glimpse(raw_lol_data)

#Skimming Data to check that there are no missing values
skimr::skim(raw_lol_data)

#Checking for duplicates in the dataset
dupes <- raw_lol_data %>% 
  janitor::get_dupes()

#Cleaning the data
clean_lol_data <- raw_lol_data %>% 
  # There are duplicate columns between the blue and the red variables, so we decided to drop the red and keep the blue
  select(-red_first_blood, -red_gold_diff, -red_experience_diff) %>% 
  # We added a column that shows the average level difference between the blue and the red teams
  mutate(avg_level_diff = blue_avg_level - red_avg_level,
         wards_diff = blue_wards_placed + blue_wards_destroyed - red_wards_placed - red_wards_destroyed,
         kill_diff = blue_kills - red_kills,
         elite_diff = blue_elite_monsters - red_elite_monsters,
         dragon_diff = blue_dragons - red_dragons,
         heralds_diff = blue_heralds - red_heralds,
         towers_diff = blue_towers_destroyed - red_towers_destroyed,
         cs_diff = blue_total_minions_killed - red_total_minions_killed,
         jg_diff = blue_total_jungle_minions_killed - red_total_jungle_minions_killed) %>% 
  
  # Changing two variables to be discrete instead of continuous 
  mutate(blue_wins = as.factor(blue_wins)) %>% 
  mutate(blue_first_blood = as.factor(blue_first_blood)) %>% 
  mutate(blue_KDA = if_else(blue_deaths > 0, (blue_kills + blue_assists)/blue_deaths, (blue_kills + blue_assists)/1L),
         red_KDA = if_else(red_deaths > 0, (red_kills + red_assists)/red_deaths, (red_kills + red_assists)/1L))

# Making sure the clean data is correct
skimr::skim(clean_lol_data)

```

```{r Aman}
# Correlations

Corr_clean_lol_data <- clean_lol_data %>%
  select(blue_wins, blue_first_blood, blue_kills, blue_deaths, avg_level_diff, blue_experience_diff)
Corr <- Corr_clean_lol_data %>% 
  GGally::ggpairs()
Corr

```

```{r linear_regression_Stephen}
# distribution of gold & exp difference by outcome
clean_lol_data %>% 
  ggplot(aes(x = blue_gold_diff, y = blue_experience_diff, color = blue_wins)) +
  geom_point() +
  theme_classic() +
  NULL

# Linear regression to predict gold_diff and exp_diff
model_linear_gold <- lm(blue_gold_diff ~ blue_first_blood + kill_diff + wards_diff + elite_diff + dragon_diff + heralds_diff + towers_diff + cs_diff + jg_diff + blue_KDA + red_KDA, data = clean_lol_data)
summary(model_linear_gold)

model_linear_exp <- lm(blue_experience_diff ~ blue_first_blood + kill_diff + wards_diff + elite_diff + dragon_diff + heralds_diff + towers_diff + cs_diff + jg_diff + blue_KDA + red_KDA, data = clean_lol_data)
summary(model_linear_exp)

plot(model_linear_gold)
plot(model_linear_exp)

# k-fold cross validation
control <- trainControl (
    method="cv",
    number=5,
    verboseIter=TRUE)

model_linear_gold_cv<-train(
    blue_gold_diff ~ blue_first_blood + kill_diff + wards_diff + elite_diff + dragon_diff + heralds_diff + towers_diff + cs_diff + jg_diff + blue_KDA + red_KDA,
    clean_lol_data,
   method = "lm",
    trControl = control
   )

summary(model_linear_gold_cv)

```

```{r Regression}
# Regression

# Starting with a simple linear regression
regression_clean_lol_data1 <- glm(blue_wins ~ blue_first_blood, data=clean_lol_data, family = "binomial")
summary(regression_clean_lol_data1)

# Multiple linear regression

regression_clean_lol_data2 <- glm(blue_wins ~ blue_first_blood + blue_kills + avg_level_diff + blue_experience_diff, data=clean_lol_data, family = "binomial")
summary(regression_clean_lol_data2)

# Logistic Regression
regression_clean_lol_data3 <- glm(blue_wins ~ blue_first_blood + blue_kills + avg_level_diff + blue_experience_diff, data=clean_lol_data, family = "binomial")
summary(regression_clean_lol_data3)

# Investigating collinearity
exp_level_differential <- glm(avg_level_diff ~ blue_experience_diff, data =clean_lol_data)
summary(exp_level_differential)

# Logistic Regression
regression_clean_lol_data4 <- glm(blue_wins ~ blue_first_blood + blue_kills + blue_experience_diff, data=clean_lol_data, family = "binomial")
summary(regression_clean_lol_data4)

# LR huge model
regression_lol5 <- glm(blue_wins ~ blue_first_blood + kill_diff + wards_diff + elite_diff + dragon_diff + heralds_diff + towers_diff + cs_diff + jg_diff + blue_KDA + red_KDA, data = clean_lol_data, family = "binomial")
summary(regression_lol5)

# Does teamwork payoff?
regression_clean_lol_data5 <- glm(blue_wins ~ blue_kills*blue_assists, data=clean_lol_data, family = "binomial")
summary(regression_clean_lol_data5)

reg_expdiff <- glm(blue_wins ~ avg_level_diff, data = clean_lol_data, family = "binomial")

plot_log <- broom::augment(reg_expdiff, type.predict = "response")
head(plot_log)

plot1 <- ggplot(plot_log, aes(x=avg_level_diff)) +
  geom_line(aes(y= .fitted), color = "blue") +
  labs(x="Experience Differential", y = "Blue Wins") +
  geom_point(aes(y=as.numeric(blue_wins)), alpha = 0.2) +
  NULL
plot1
```

```{r Sarah}
clean_lol_data %>% ggplot(aes(x = blue_gold_per_min, y = blue_assists, colour = factor(blue_wins), fill = factor(blue_wins))) +
  geom_point(alpha = 0.1) +
  geom_jitter(width = 0.25) +
  scale_colour_manual(values = c("red", "blue"),
                      # breaks=c("0","1"),
                      labels=c("Red Team Wins", "Blue Team Wins")) +
  theme_minimal() +
  labs(
    title = "More Assists and Higher Gold Rate Lead to More Wins for Blue Team",
    subtitle = "Assists by Blue Team vs. Gold Difference",
    y = "Number of Assists",
    x = "Gold Per Minute")+
  theme(legend.title=element_blank())
```

```{r}
clean_lol_data %>% ggplot(aes(x = blue_kills, y = blue_assists, colour = factor(blue_wins), fill = factor(blue_wins))) +
  geom_point(alpha = 0.8, size = 0.9) +
  geom_jitter() +
  scale_colour_manual(values = c("red", "blue"),
                      # breaks=c("0","1"),
                      labels=c("Red Team Wins", "Blue Team Wins")) +
  theme_minimal() +
  labs(
    title = "More Assists and Higher Gold Rate Lead to More Wins for Blue Team",
    subtitle = "Assists by Blue Team vs. Gold Difference",
    y = "Number of Assists",
    x = "Number of Kills")+
  theme(legend.title=element_blank())
```

```{r}
clean_lol_data %>% group_by(blue_wins) %>% 
  summarise(
            # avg_wards_placed = mean(blue_wards_placed), 
            # avg_wards_destroyed = mean(blue_wards_destroyed), 
            # avg_minions = mean(blue_total_minions_killed),
            avg_elite_monsters = mean(blue_elite_monsters), 
            avg_dragons = mean(blue_dragons), 
            avg_heralds = mean(blue_heralds), 
            avg_towers_destroyed = mean(blue_towers_destroyed)) %>% 
  pivot_longer(cols = c(
            # avg_wards_placed, avg_wards_destroyed, 
            # avg_minions,
            avg_elite_monsters, avg_dragons, avg_heralds, avg_towers_destroyed), 
               names_to = "feature", 
               values_to = "value") %>% 
  ggplot(.,aes(x = feature, y = value)) + 
  geom_col(aes(fill = blue_wins), position = "dodge") +
  scale_fill_manual(values = c("#e63946","#0466c8"), labels=c("Red Team Wins", "Blue Team Wins"))+
  theme_minimal() +
  coord_flip() + 
  labs(
    title = "Towers Destroyed is the Most Significant Determinant",
    subtitle = "Number of Kills and Detroys for All Objects in Game",
    y = "Average Number of Kills/Destroys",
    x = "")+
   theme(
    text=element_text(size=12, family="Lato"),
    plot.title =element_text(face='bold'),
    plot.subtitle = element_text(face='italic', size=10),
    axis.text = element_text(angle = 0, hjust = 0.5, size = 10),
    legend.title=element_blank()
  ) 
```

```{r}
  ggplot(.,aes(x = feature, y = value)) + 
  geom_col(aes(fill = blue_wins), position = "dodge") +
  scale_fill_manual(values = c("red","blue"), labels=c("Red Team Wins", "Blue Team Wins"))+
  theme_minimal() +
  labs(
    title = "Towers Destroyed is the Most Significant Determinant",
    subtitle = "Number of Kills and Detroys for All Objects in Game",
    y = "Average Number of Kills/Destroys",
    x = "")+
  theme(legend.title=element_blank())
```

```{r}
clean_lol_data %>% 
  pivot_longer(cols = c("elite_diff","dragon_diff", "heralds_diff", "towers_diff"), names_to = "feature", values_to = "value") %>% 
  ggplot(.,aes(x = feature, y = value)) +
  geom_violin(aes(fill = feature)) +
  scale_fill_brewer(palette = 1)
  theme_minimal() +
  labs(
    title = "",
    subtitle = "Distribution of Activity Differences",
    y = "",
    x = "")+
  theme(legend.title=element_blank())
  
```
